Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-02-05 ECCV/paper.tex
Details about algorithm

\section{Related Work}
ARToolkit \cite{ARToolkit02} /ARTag \cite{Fiala05} \\
Pi-Tag \cite{Pitag13} \\
Blut \cite{Wu:2011}

@@

\subsection{Fiducial Detection Algorithm}
Apply Gabor Filter on input image \\
Find Connected components in Gabor output \\
Cluster the connected components \\
Merge the clusters \\
Detect code in the bounding box \\
Classify the detected code

\section{Experimental Results}

@@

\section{Future Work}

\bibliographystyle{splncs}
\bibliography{egbib}

>>>>

\section{Related Work}
ARToolkit \cite{ARToolkit02} \cite{kato-artoolkit} /ARTag \cite{Fiala05} \\
Circular Data Matrix Fiducial System \cite{NaimarkF02} \\
Reliable Fiducial Detection in Natural Scenes \cite{ClausF04}\\
RUNE-Tag \cite{runetag11} \\
Pi-Tag \cite{Pitag13} \\
Blut \cite{Wu:2011}

@@

\subsection{Fiducial Detection Algorithm}
\begin{itemize}
  \item Apply Gabor Filter on input image
  \item Find Connected components in Gabor output
  \item Cluster the connected components in bounding box
  \item Detect code in the bounding box
  \begin{itemize}
    \item Run PCA on Gabor output in bounding box
    \item Find intensity profile along first principal component passing through
    centroid
    \item If there are less than four black to white transitions in the
    intensity profile, ignore the bouding box
    \item Otherwise, classify the detected code by the classifer trained on
    standards.
  \end{itemize}
\end{itemize}

\section{Experimental Results}
\subsection{Comparison}
We will compare our results with standard fiducials such as ARTag. Also, we will
compare our results with Blur driven tracker.
\subsubsection{Comparison with ARTag}
\subsubsection{Comparison with Blut}

@@

\section{Future Work}
Pose Estimation
\bibliographystyle{splncs}
\bibliography{egbib}
